Empirical Analysis of Performance Bottlenecks in Graph Neural Network Training and Inference with GPUs

### 2021-02-22 NEUROC/Response-MinorRev/response_letter-minor-rev.tex

\section*{Response to the Reviewers}
% General intro text goes here
We thank the reviewers for their insightful comments on our work.
%
We have made modifications to our manuscript according to Reviewer 1's comments.

% Let's start point-by-point with Reviewer 1
\reviewersection

% R1Q0
\begin{point}
    In the revised manuscript, the authors have addressed all my concerns, especially adding more computation efficiency discussion. Current version looks very impressive. Just a small issue left. Some discussions about limitations or future efforts should be better added.
\end{point}

\begin{reply}
    Thank you for the insightful suggesion.
    %
    According to the suggestion, we have added a paragraph at the end of Section 7 ``Conclusion and Future Work'' to discuss limitations of our work and points out potential future research directions.
    %
    In this work, we mainly analyze performance bottlenecks of GNN training/inference in a \emph{single-GPU} environment on \emph{static} graphs with the \emph{message-passing} framework.
    %
    Performance bottlenecks in \emph{multi-GPU}/\emph{distributed} GNN training/inference with \emph{dynamic} graphs and \emph{other} GNN frameworks are also worth studying.
    %
    In the future, we plan to extend our work in the following directions:
    %
\begin{enumerate}
    \item \emph{Multi-GPU and distributed GNN training/inference.}
    %
    To handle large-scale graph datasets, training/inferring GNNs with multiple GPUs or in a distributed environment is necessary.
    %
    Multi-GPU and distributed GNN training/inference will inevitably introduce overheads such as inter-GPU and inter-machine communication. 
    %
    How these overheads affect performance bottlenecks is worthy to focus on.
    %
    \item \emph{Spatial-temporal graph datasets.}
    %
    Spatial-temporal graphs have dynamic topology structures.
    %
    They appear in a variety of applications like traffic speed forecasting [\cite{li2018_DCRNN}] and human action recognition [\cite{yan2018_STGCN}].
    %
    %Learning hidden patterns from spatial-temporal graphs become increasingly important.
    %
    Many new GNNs are proposed to handle this kind of dynamic graphs.
    %
    How the performance bottlenecks of these GNNs are different from the classic GNNs is also worthy of in-depth study.
    %
    %Whether spatial-temporal graphs will affect performance is worthy of our attention.
    %
    \item \emph{Other GNN frameworks.}
    %
    In this work, we conducted analysis with the message-passing framework that is popular among existing GNN learning systems.
    %
    Some emerging GNN learning systems also adopt different frameworks like SAGA framework [\cite{ma2019_neugraph}] and edge-centric framework [\cite{he2019_EnGN}].
    %
    Whether different frameworks lead to different performance bottlenecks is worth further investigation.
\end{enumerate}

\end{reply}

### 2021-02-22 NEUROC/sec7-conclusion.tex
更新response letter和正文.

In this work, we analyze performance bottlenecks in a \emph{single-GPU} environment on \emph{static} graphs with the \emph{message-passing} framework.
%
Performance bottlenecks in multi-GPU/distributed GNN training/inference with dynamic graphs and other GNN frameworks are also worth studying.
%
In the future, we plan to extend our analysis of performance bottlenecks in GNN training/inference with the following directions:
%
\begin{enumerate}
    \item \emph{Multi-GPU and distributed GNN training/inference.}
    %
    To handle large-scale graph datasets, multi-GPU and distributed training/inference are necessary.
    %
    These methods will inevitably introduce overheads such as inter-GPU and inter-machine communication. 
    %
    How these overheads affect performance bottlenecks is worthy to focus on.
    %
    \item \emph{Spatial-temporal graph datasets.}
    %
    Spatial-temporal graphs have dynamic topology structures.
    %
    They appear in a variety of applications like traffic speed forecasting \cite{li2018_DCRNN} and human action recognition \cite{yan2018_STGCN}.
    %
    %Learning hidden patterns from spatial-temporal graphs become increasingly important.
    %
    Many new GNNs are proposed to handle this kind of graph.
    %
    How the performance bottlenecks of these GNNs are different from the classic GNNs is also worthy of in-depth study.
    %
    %Whether spatial-temporal graphs will affect performance is worthy of our attention.
    %
    \item \emph{Other GNN frameworks.}
    %
    In this work, we analyzed with the popular message-passing framework of GNNs.
    %
    Some emerging GNN learning systems also adopt different GNN frameworks like SAGA framework \cite{ma2019_neugraph} and edge-centric framework \cite{he2019_EnGN}.
    %
    Whether different frameworks lead to different performance bottlenecks is worth discussing.
\end{enumerate}

>>>>

\paragraph{Future Work}

In this work, we analyze performance bottlenecks in a \emph{single-GPU} environment on \emph{static} graphs with the \emph{message-passing} framework.
%
Performance bottlenecks in multi-GPU/distributed GNN training/inference with dynamic graphs and other GNN frameworks are also worth studying.
%
In the future, we plan to extend our analysis of performance bottlenecks in the following directions:
%
\begin{enumerate}
    \item \emph{Multi-GPU and distributed GNN training/inference.}
    %
    To handle large-scale graph datasets, training/inferring GNNs with multiple GPUs or in a distributed environment is necessary.
    %
    Multi-GPU and distributed GNN training will inevitably introduce overheads such as inter-GPU and inter-machine communication. 
    %
    How these overheads affect performance bottlenecks is worthy to focus on.
    %
    \item \emph{Spatial-temporal graph datasets.}
    %
    Spatial-temporal graphs have dynamic topology structures.
    %
    They appear in a variety of applications like traffic speed forecasting \cite{li2018_DCRNN} and human action recognition \cite{yan2018_STGCN}.
    %
    %Learning hidden patterns from spatial-temporal graphs become increasingly important.
    %
    Many new GNNs are proposed to handle this kind of dynamic graphs.
    %
    How the performance bottlenecks of these GNNs are different from the classic GNNs is also worthy of in-depth study.
    %
    %Whether spatial-temporal graphs will affect performance is worthy of our attention.
    %
    \item \emph{Other GNN frameworks.}
    %
    In this work, we conducted analysis with the message-passing framework that is popular among existing GNN learning systems.
    %
    Some emerging GNN learning systems also adopt different frameworks like SAGA framework \cite{ma2019_neugraph} and edge-centric framework \cite{he2019_EnGN}.
    %
    Whether different frameworks lead to different performance bottlenecks is worth further investigation.
\end{enumerate}
